Self-test prime dimensional EPR pairs with constant alphabet

### 2019-02-01 Draft/draft.tex
Honghao: minor modifications

The set $D$ is easily characterizable as it contains all the odd prime numbers with 
primitive root $2$, $3$ or $5$. It has been shown that there are infinitely many prime numbers
with primitive root in the set $\{2,3,5\}$ \cite{murty1988}, so the set $D$ has infinitely many elements.
To prove \cref{thm:inf}, we give explicit self-testing proof of 
the maximally entangled state with local dimension $d-1$ where the primitive root of $d$ is $2$ by explicitly giving the 
correlation that achieves this goal. Then the self-testing property of this correlation is 
given in the following theorem.
\begin{theorem}[Informal]
\label{thm:pr_2}
	All maximally entangled state with local dimension $d-1$, where $d$ is prime and has
	primitive root $r \in \{2, 3, 5\}$, can be self-tested by a constant-sized correlation.
\end{theorem}
The correlation that we use to prove \cref{thm:pr_2} is denoted by $C(\dr{r})$.
We use the superscript $(r)$ to denote the primitive root of $d$.
Note that although the size of $C(\dr{r})$ does not depend on $d$, the optimal correlation does.

In order to accomplish our goal, we introduce new techniques for self-testing.
First of all, we use a different variant of the weighted CHSH inequality to enforce the eigenvalue of
some unknown operator which is decomposed into two binary observables, which is not done before.
Secondly, we give a new way to decompose unitaries of arbitrary order into binary observables which maintain
certain commutation relations. Such decomposition is different from what Slofstra used in his work \cite{slofstra2017}.
Intuitively, such decomposition can be seen as the inverse of the decomposition used in the proof of Jordan's lemma.
The third contribution is that we prove self-testing without using anti-commutation relations between Pauli operators, 
which is the core idea in all the previous self-testing results. 
Instead, we find a new pair of operators that can generate the ring of matrices over complex numbers.

\textbf{Structure of the paper}.
We start with notations and background information in \cref{sec:prelim}.
Since the game we designed consists of two sub-tests, we introduce one test
in \cref{sec:lsg} and one in \cref{sec:chsh}. Our main result is based the combination
of the sub-tests and presented in \cref{sec:main}. In \cref{sec:extend}, we show how to adapt
our nonlocal game to self-test maximally entangled state of different dimensions.

@@

We use some basic number theory concepts in our work. A primitive root of a prime number
$d$ is an integer $r$ such that $r \pmod{d}$ has multiplicative order $d-1$. Equivalently,
$r$ is the generator of the multiplicative group of integers modulo $d$, $\Z_d^\times$ where
$\Z_d^\times = \{1,2\dots d-1\}$.
The EPR pair of local dimension $d-1$ for some prime $d$, which has primitive root $2$, 
is denoted by
\begin{align}
\ket{\EPR{d-1}} = \frac{1}{\sqrt{d-1}} \sum_{i = 0}^{d-2} \ket{ii}.
\end{align}
The superscript $(d-1)$ stresses the local dimension and we follow this convention through this paper.

We self-test $\ket{\EPR{d-1}}$ by verify that Alice and Bob has operators
\begin{align}
	X = \sum_{k=1}^{d-1} \omega_d^k\ketbra{k}{k} && U = \sum_{k=1}^{d-1} \ketbra{k/r}{k},
\end{align}
where $\omega_d = e^{i2\pi/d}$ is the primitive $d$-th root of unity,
and $r$ is the primitive root of $d$.
Through out this paper, any operation on the label of the eigenvector $\ket{i}$ is taken modulo $d$,
unless otherwise specified, for example, the $i/r$ above.

\textbf{The weighted CHSH inequality \cite{acin2012}.}
The first building-block of our result is a robust self-testing result based on the weighted CHSH inequality.
In the CHSH scenario, Alice and Bob has binary observables $A_x,B_y$ for $x,y = 1,2$ 
on Hilbert space $\calH_A$ and $\calH_B$ respectively.
A binary observable is a Hermitian matrix whose eigenvalues are either $+1$ or $-1$.
The weighted CHSH inequality is given by 
\begin{align}
	\label{eq:chsh_op}
	\I_\alpha = \alpha\ip{A_1B_1}+\alpha\ip{A_1B_2} + \ip{A_2B_1} - \ip{A_2B_2}\leq 2\alpha,
\end{align}
where $\ip{A_xB_y}$ is the expectation value of of the observables.
If Alice and Bob share product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$, they cannot violate
the weighted CHSH inequality.
However, If they share entangled state $\ket{\psi}$, the maximal violation is 
\begin{align}
\label{eq:chsh_max}
 \I_\alpha \leq 2\sqrt{1+\alpha^2}.
\end{align}
\begin{definition}[Ideal strategy for $\I_\alpha$]
	\label{def:ideal}
	Define $\mu = \arctan(1/\alpha)$.
	The ideal strategy for weighted CHSH with parameter $\alpha$ (i.e. achieving maximal violation in \cref{eq:chsh_max})
	consists of the joint state $\ket{\EPR{2}}$ and observables $A_1 = \pauliz$, $A_2 = \paulix$,
	$B_1 = \cos(\mu) \pauliz+ \sin(\mu) \paulix$ and $B_2 = \cos(\mu) \pauliz - \sin(\mu) \paulix$.
\end{definition}
An interesting observation of the weighted CHSH inequality is that its maximal violation can certify the shared states and the 
measurements, which is the phenomenon of self-test. We give formal statement of this self-test result in \cref{sec:chsh}.

\textbf{Nonlocal games}. The two players of a nonlocal game are Alice and Bob. Each of them is requested
to give an answer for a randomly chosen question. We denote Alice's question set by $\calX$ and answer set by $\calA$. Similarly,
Bob's question set is denoted by $\calY$ and his answer set is denoted by $\calB$. The nonlocal game also
comes with two functions: $\pi: \calX \times \calY \rightarrow [0,1]$, which is the probability distribution over the questions,
and $V: \calA \times \calB \times \calX \times \calY \rightarrow \R$, which is the scoring function. Such games are nonlocal
because Alice and Bob cannot communicate after getting their questions but they may share some strategy before 
the start of the game. Note that in the literature, the typical scoring function of a nonlocal game maps the input-output
pair to $\{0.1\}$ which corresponds to losing and winning. Allowing the score to be any real number is the key ingredient 
to our new nonlocal game.

The quantum strategy of a game $G$ consists of projective measurements $\{\{A_x^a\}_a\}$ on Alice's side and 
$\{\{B_y^b\}_b\}_y$ on Bob's side, and a shared state $\ket{\psi}$. Then the behaviour of Alice and Bob is described 
by the conditional probability
\begin{align}
	\pr{ab}{xy} = \bra{\psi} A_x^a \x B_y^b \ket{\psi} \text{ for all } (a,b,x,y) \in \calA \times \calB \times \calX \times \calY,
\end{align}
where $(A_x^a)^2 = A_x^a = (A_x^a)^\dagger$ and $(B_y^b)^2 = B_y^b = (B_y^b)^\dagger$.
Note that we may use the term behaviour and correlation interchangeably.
The \emph{value} of a strategy is given by
\begin{align}
	\omega(G,p)  = \sum_{a,b,x,y} \pi(x,y) \pr{ab}{xy} V(a,b,x,y).
\end{align}

The main contribution of our work is the construction of a correlation, which is the optimal correlation of a game $\G$ with constant-sized $\calX$,$\calY$,$\calA$ and $\calB$
such that this correlation can self-test $\ket{\EPR{d-1}}$ for arbitrary $d \in D$. 
The nonlocal game $\G$ is a linear system game with strict enforcements. 
We introduce the definition of self-testing first, the definition of linear system game, 
and its operator solution, 
following definitions given in Ref.~\cite{coladan2017, slofstra2017}.
\begin{definition}[Self-testing]
	We say that a correlation self-tests a quantum state $\ket{\psi}$, if 
	the correlation is produced by a strategy with shared state $\ket{\psi}$, and 
	for any quantum strategy $S = ( \{\tA_x\}, \{\tB_y\}, \ket{\tpsi})$ that produces the same correlation,
	there exists local isometries $\Phi_A$ and $\Phi_B$ on Alice and Bob's side and a state $\ket{junk}$ 
	such that 	
	\begin{align*}
		\Phi_A \x \Phi_B \ket{\tpsi} =  \ket{\psi} \x \ket{junk}.
	\end{align*}
\end{definition}
\begin{definition}[Linear system game]
 Let $Hx = c$ be an $m \times n$ system of linear equations over $\Z_2$,
 where $H$ is an $m$-by-$n$ matrix with entries in $\Z_2 = \{0,1\}$ and 
 $c$ is a length-$n$ vector with entries in $\Z_2$ too. 
 The associated linear system game involves two
 players Alice and Bob, where Alice is given an equation number $i \in \calX = [m]+1$ and replies with $a \in \calA = \Z_2^{\times n}$,
 and Bob is given a variable number $j \in \calY = [n]+1$ and replies with an assignment $b \in \calB = \Z_2$. The winning condition is 
 that Alice's assignment to the variables should satisfy equation $i$ and Alice's $j$-th assignment $a(j)$ should match $b$.
 Formally, the winning condition is 
 \begin{align*}
 	a(j) &= b && \text{(Consistency)} \\
	\sum_{k= 1}^n H(i,k) a(k) &\equiv c(i) \pmod 2. &&\text{(Constraint satisfaction)},
 \end{align*}
 for all $(i,j) \in \calX \times \calY$.
\end{definition}
The scoring function of linear system games always maps an input-output pair to $\{0,1\}$, 
so later when we say a quantum strategy wins a linear system game perfectly, we mean that 
$V(a,b,x,y) =0$ implies that $\pr{ab}{xy} = 0$.
We focus on quantum strategies for the linear system game presented in terms of binary observables.
\begin{definition}[Quantum strategy of a linear system game]
\label{def:q_strat}
A quantum strategy for the linear system game $(Hx = c)$ consists of 
\begin{enumerate}
	\item a pair of finite Hilbert spaces $\calH_A$ and $\calH_B$;
	\item a collection of binary observables $B_j$, $1 \leq j \leq n$, on $\calH_B$
	such that $B_j^2 = \1$ for every $1 \leq j \leq n$;
	\item a collection of binary observables $A_{ij}$, $1\leq i \leq m$, $1\leq j\leq n$ 
	on $\calH_A$ such that 
	\begin{enumerate}
		\item $A_{ij}^2 = \1$ for every $i,j$,
		\item $\Pi_j A_{ij}^{H(i,j)} = (-\1)^{c(i)}$ for every $i$, and
		\item $A_{il}A_{ik} = A_{ik}A_{il}$ for every $i$ and $H(i,l) = H(i,k) =1$;
	\end{enumerate} 
	and
	\item a quantum state $\ket{\psi} \in \calH_A \x \calH_B$.
\end{enumerate}
\end{definition}
Note that any quantum strategy presented in terms of binary observables can be 
converted to a quantum strategy presented in terms of projective measurement, and
vice versa.

@@

Slofstra's seminal work~\cite{slofstra2017} draws our attention to the relation $xyx^{-1} = y^2$.
The main component of $\G(\dr{r})$ is a linear system game $\LS$, whose solution group is the embedding of the 
following group
\begin{align}
	\Pg_r= \langle u, x : uxu^{-1} = x^r \rangle, \text{ for } r \in \{2, 3,5\}.
\end{align}
In other words, relations in the presentation of the solution group of $\LS$ can be combined to derive the
relation $uxu^{-1} = x^r$.
\begin{proposition}
	\label{prop:embed}
	The group $\Pg_r$ can be embedded into a linear system game $\LS$ over $\Z_2$,
	with constant numbers of variables and equations, where each equation involves $3$ variables.
\end{proposition}
The process of embedding $\Pg_r$ into the solution group of $\LS$ follows the recipe given in the proofs of
Proposition~$4.8$, Lemma~$4.4$ and Proposition $4.2$ of Slofstra's seminal work \cite{slofstra2017}.
The order of applying the results is the reverse of the order they are presented in Ref.~\cite{slofstra2017}.
We give details of this embedding process in \cref{sec:power2} for $r = 2$, \cref{sec:power3} for $r = 3$, 
and \cref{sec:power5} for $r = 5$.

@@

We start with proving that $\ket{x_{k_1}} = 0$.
Proving $\ket{x_{k_i}} = 0$ for other $i$ follows a similar argument, so we briefly
discuss about it in the end.
The entry $\bra{1}M\ket{1}$ can be expressed as  
\begin{align}
	\bra{1}M\ket{1} = \sum_{k=0}^{d-2}\sum_{l = 1}^{d-1}\sum_{i=1}^{d-1} x_{k, l}\omega_d^{il}\braket{1}{i/r^k}\braket{i}{1}.
\end{align}
For the term $\braket{1}{i/r^k}\braket{i}{1} \neq 0$ we must have $i = 1$ and $r^k \equiv 1 \pmod{d}$, or equivalently,
$k = k_1$. Hence, we can conclude that 
\begin{align}
	\bra{1}M\ket{1} = \sum_{l = 1}^{d-1} x_{k_1,l}\omega_d^l = 0. 
\end{align}
Similarly we can determine that for all $j = 1,2\dots d-1$,
\begin{align}
	\bra{j}M\ket{j} 
	=  \sum_{k=0}^{d-2}\sum_{l = 1}^{d-1}\sum_{i=1}^{d-1} x_{k, l}\omega_d^{il}\braket{j}{i/r^k}\braket{i}{j} 
	= \sum_{l = 1}^{d-1}x_{k_1,l}\omega_d^{jl} = 0.
\end{align}
Hence we get $d-1$ equations with $d-1$ variables, and the linear system is
\begin{align}
	W \ket{x_{k_1}} = 0,
\end{align}
where $W_{m,n} = \omega_d^{mn}$. Then we define
\begin{align}
	\tW = 
	\begin{pmatrix}
	1 & 1 \\
	1 & W
	\end{pmatrix}.
\end{align}
First observe that $\tW$ is a Vandermonde matrix, hence it is non-singular.
Next, we define $\ket{\tx_{k_1}} = (0, x_{k_1,1}, \dots x_{k_1,d-1})^\intercal$ 
and prove that it satisfies the condition
that 
\begin{align}
	\tW \ket{\tx_{k_1}} = 0,
\end{align}
which involves $d$ equations. The last $d-1$ equations are given by the assumption and $M$.
We only need to prove that $\sum_{l=1}^d x_{k_1, l} = 0$, which is required by the first row of $\tW$.
It can be proved by summing the known $d-1$ equations as follows
\begin{align}
	0=\sum_{j = 1}^{d-1} \bra{j}M\ket{j}  
	=  \sum_{j=1}^{d-1}\sum_{l = 1}^{d-1}x_{k_1,l}\omega_d^{jl}
	=\sum_{l = 1}^{d-1}x_{k_1,l} (\sum_{j=1}^{d-1} \omega_d^{jl})
	= \sum_{l = 1}^{d-1}- x_{k_1,l}
\end{align}
where we have used the fact that $\sum_{j=1}^{d-1} \omega_d^{jl} =-1$ for all $l = 1,2\dots d-1$.
Since $\tW$ is non-singluar, we know $\ket{\tx_{k_1}} = 0$ which implies that $\ket{x_{k_1}} = 0$.

>>>>

The set $D$ is easily characterizable as it contains all the odd prime numbers with 
primitive root $2$, $3$ or $5$. It has been shown that there are infinitely many prime numbers
with primitive root in the set $\{2,3,5\}$ \cite{murty1988}, so the set $D$ has infinitely many elements.
To prove \cref{thm:inf}, we give explicit self-testing proof of 
the maximally entangled state with local dimension $d-1$ where the primitive root of $d$ is $2$,$3$, or $5$, 
by explicitly giving the correlation that achieves self-testin. 
%Then the self-testing property of this correlation is 
%given in the following theorem.
%\begin{theorem}[Informal]
%\label{thm:pr_2}
%	All maximally entangled state with local dimension $d-1$, where $d$ is prime and has
%	primitive root $r \in \{2, 3, 5\}$, can be self-tested by a constant-sized correlation.
%\end{theorem}
Our correlation is denoted by $C(\dr{r})$ for prime $d$.
We use the superscript $(r)$ to denote the primitive root of $d$.
Note that although the size of $C(\dr{r})$ does not depend on $d$, the optimal correlation does.

In order to accomplish our goal, we introduce new techniques for self-testing.
First of all, we use a different variant of the weighted CHSH inequality to enforce the eigenvalue of
some unknown operator which is decomposed into two binary observables.
The variant of the CHSH inequality that we use is not used in the self-testing literature befor.
Secondly, we give a new way to decompose unitaries of arbitrary order into binary observables which maintain
certain commutation relations. Such decomposition is different from what Slofstra used in his work \cite{slofstra2017}.
Intuitively, such decomposition can be seen as the inverse of the decomposition used in the proof of Jordan's lemma.
The third contribution is that we prove self-testing without using anti-commutation relations between Pauli operators, 
which is the core idea in all the previous self-testing results. 
Instead, we find a new pair of operators that can generate the ring of matrices over complex numbers.

\textbf{Structure of the paper}.
We start with notations and background information in \cref{sec:prelim}.
Since the correlation we designed satisfies two sub-tests, we introduce one test
in \cref{sec:lsg} and the other one in \cref{sec:chsh}. Our main result is based on the combination
of the sub-tests and presented in \cref{sec:main}.

@@

We use some basic number theory concepts in our work. A primitive root of a prime number
$d$ is an integer $r$ such that $r \pmod{d}$ has multiplicative order $d-1$. Equivalently,
$r$ is the generator of the multiplicative group of integers modulo $d$, $\Z_d^\times$ where
$\Z_d^\times = \{1,2\dots d-1\}$.
The EPR pair of local dimension $d-1$ for some prime $d$ is denoted by
\begin{align}
\ket{\EPR{d-1}} = \frac{1}{\sqrt{d-1}} \sum_{i = 0}^{d-2} \ket{ii}.
\end{align}
The superscript $(d-1)$ stresses the local dimension and we follow this convention through this paper.

We self-test $\ket{\EPR{d-1}}$ by verify that Alice and Bob has operators
\begin{align}
	X = \sum_{k=1}^{d-1} \omega_d^k\ketbra{k}{k} && U = \sum_{k=1}^{d-1} \ketbra{k/r}{k},
\end{align}
where $\omega_d = e^{i2\pi/d}$ is the primitive $d$-th root of unity,
and $r$ is the primitive root of $d$.
Through out this paper, any operation on the label of the eigenvector $\ket{k}$ is taken modulo $d$,
unless otherwise specified, for example, the $k/r$ above.

\textbf{The weighted CHSH inequality \cite{acin2012}.}
The first building-block of our result is a robust self-testing result based on the weighted CHSH inequality.
In the CHSH scenario, Alice and Bob has binary observables $A_x,B_y$ for $x,y = 1,2$ 
on Hilbert space $\calH_A$ and $\calH_B$ respectively.
A binary observable is a Hermitian matrix whose only eigenvalues are either $+1$ or $-1$.
The weighted CHSH inequality is given by 
\begin{align}
	\label{eq:chsh_op}
	\I_\alpha = \alpha\ip{A_1B_1}+\alpha\ip{A_1B_2} + \ip{A_2B_1} - \ip{A_2B_2}\leq 2\alpha,
\end{align}
where $\ip{A_xB_y}$ is the expectation value of of the observables.
If Alice and Bob share product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$, they cannot violate
the weighted CHSH inequality.
However, If they share entangled state $\ket{\psi}$, the maximal violation is 
\begin{align}
\label{eq:chsh_max}
 \I_\alpha \leq 2\sqrt{1+\alpha^2}.
\end{align}
\begin{definition}[Ideal strategy for $\I_\alpha$]
	\label{def:ideal}
	Define $\mu = \arctan(1/\alpha)$.
	The ideal strategy for weighted CHSH with parameter $\alpha$ (i.e. achieving maximal violation in \cref{eq:chsh_max})
	consists of the joint state $\ket{\EPR{2}}$ and observables $A_1 = \pauliz$, $A_2 = \paulix$,
	$B_1 = \cos(\mu) \pauliz+ \sin(\mu) \paulix$ and $B_2 = \cos(\mu) \pauliz - \sin(\mu) \paulix$.
\end{definition}
An interesting observation of the weighted CHSH inequality is that its maximal violation can certify the shared states and the 
measurements, which is a phenomenon referred as a self-test. We give formal statement of this self-testing result in \cref{sec:chsh}.

\textbf{Nonlocal games}. The two players of a nonlocal game are Alice and Bob. Each of them is requested
to give an answer for a randomly chosen question. We denote Alice's question set by $\calX$ and answer set by $\calA$. Similarly,
Bob's question set is denoted by $\calY$ and his answer set is denoted by $\calB$. The nonlocal game also
comes with two functions: $\pi: \calX \times \calY \rightarrow [0,1]$, which is the probability distribution over the questions,
and $V: \calA \times \calB \times \calX \times \calY \rightarrow \R$, which is the scoring function. Such games are nonlocal
because Alice and Bob cannot communicate after getting their questions but they may share some strategy before 
the start of the game. Note that in the literature, the typical scoring function of a nonlocal game maps the input-output
pair to $\{0.1\}$ which corresponds to losing and winning. Allowing the score to be any real number is the key ingredient 
to our new result.

A quantum strategy of a game $G$ consists of projective measurements $\{\{A_x^a\}_a\}$ on Alice's side, 
$\{\{B_y^b\}_b\}_y$ on Bob's side, and a shared state $\ket{\psi}$, where a projective measurement $P$ satisfies
the condition that $P^2 = P = P\ct$.
Then Alice and Bob's quantum strategy produces the correlation
\begin{align}
	\pr{ab}{xy} = \bra{\psi} A_x^a \x B_y^b \ket{\psi} \text{ for all } (a,b,x,y) \in \calA \times \calB \times \calX \times \calY,
\end{align}
where $(A_x^a)^2 = A_x^a = (A_x^a)^\dagger$ and $(B_y^b)^2 = B_y^b = (B_y^b)^\dagger$.
%Note that we may use the term behaviour and correlation interchangeably.
%The value of a strategy is given by
%\begin{align}
%	\omega(G,p)  = \sum_{a,b,x,y} \pi(x,y) \pr{ab}{xy} V(a,b,x,y).
%\end{align}

The main contribution of our work is the construction of a correlation, which is the optimal correlation of a nonlocal game $\G$ with constant-sized $\calX$,$\calY$,$\calA$ and $\calB$
such that this correlation can self-test $\ket{\EPR{d-1}}$ for arbitrary $d \in D$. 
The nonlocal game $\G$ is a linear system game with strict enforcements. 
We introduce the definition of self-testing, the definition of linear system game, 
and its operator solution, 
following definitions given in Ref.~\cite{coladan2017, slofstra2017}.
\begin{definition}[Self-testing]
	We say that a correlation self-tests a quantum state $\ket{\psi}$, if 
	the correlation is produced by a strategy with shared state $\ket{\psi}$, and 
	for any quantum strategy $S = ( \{\tA_x\}, \{\tB_y\}, \ket{\tpsi})$ that produces the same correlation,
	there exists local isometries $\Phi_A$ and $\Phi_B$ on Alice and Bob's side and a state $\ket{junk}$ 
	such that 	
	\begin{align*}
		\Phi_A \x \Phi_B \ket{\tpsi} =  \ket{\psi} \x \ket{junk}.
	\end{align*}
\end{definition}
\begin{definition}[Linear system game]
 Let $Hx = c$ be an $m \times n$ system of linear equations over $\Z_2$,
 where $H$ is an $m$-by-$n$ matrix with entries in $\Z_2 = \{0,1\}$ and 
 $c$ is a length-$n$ vector with entries in $\Z_2$. 
 The associated linear system game involves two
 players Alice and Bob, where Alice is given an equation number $i \in \calX = [m]+1$ and replies with $a \in \calA = \Z_2^{\times n}$,
 and Bob is given a variable number $j \in \calY = [n]+1$ and replies with an assignment $b \in \calB = \Z_2$. The winning condition is 
 that Alice's assignment to the variables should satisfy equation $i$ and Alice's $j$-th assignment $a(j)$ should match $b$.
 Formally, the winning condition is 
 \begin{align*}
 	a(j) &= b && \text{(Consistency)} \\
	\sum_{k= 1}^n H(i,k) a(k) &\equiv c(i) \pmod 2. &&\text{(Constraint satisfaction)},
 \end{align*}
 for all $(i,j) \in \calX \times \calY$.
\end{definition}
The scoring function of linear system games always maps an input-output pair to $\{0,1\}$, 
so later when we say a quantum strategy wins a linear system game perfectly, we mean that 
$V(a,b,x,y) =0$ implies that $\pr{ab}{xy} = 0$.
We focus on quantum strategies for the linear system game presented in terms of binary observables.
\begin{definition}[Quantum strategy of a linear system game]
\label{def:q_strat}
A quantum strategy for the linear system game $(Hx = c)$ consists of 
\begin{enumerate}
	\item a pair of finite Hilbert spaces $\calH_A$ and $\calH_B$;
	\item a collection of binary observables $B_j$, $1 \leq j \leq n$, on $\calH_B$
	such that $B_j^2 = \1$ for every $1 \leq j \leq n$;
	\item a collection of binary observables $A_{ij}$, $1\leq i \leq m$, $1\leq j\leq n$ 
	on $\calH_A$ such that 
	\begin{enumerate}
		\item $A_{ij}^2 = \1$ for every $i,j$,
		\item $\Pi_j A_{ij}^{H(i,j)} = (-\1)^{c(i)}$ for every $i$, and
		\item $A_{il}A_{ik} = A_{ik}A_{il}$ for every $i$ and $H(i,l) = H(i,k) =1$;
	\end{enumerate} 
	and
	\item a quantum state $\ket{\psi} \in \calH_A \x \calH_B$.
\end{enumerate}
\end{definition}
Note that any quantum strategy presented in terms of binary observables can be 
converted to a quantum strategy presented in terms of projective measurement, and
vice versa.

@@

Slofstra's seminal work~\cite{slofstra2017} draws our attention to the relation $xyx^{-1} = y^2$.
The main component of $\G(\dr{r})$ is a linear system game $\LS$, whose solution group is the embedding of the 
following group
\begin{align}
	\Pg_r= \langle u, x : uxu^{-1} = x^r \rangle, \text{ for } r \in \{2, 3,5\}.
\end{align}
In other words, relations in the presentation of the solution group of $\LS_r$ can be combined to derive the
relation $uxu^{-1} = x^r$.
\begin{proposition}
	\label{prop:embed}
	The group $\Pg_r$ can be embedded into a linear system game $\LS_r$ over $\Z_2$,
	with constant numbers of variables and equations, where each equation involves $3$ variables.
\end{proposition}
The process of embedding $\Pg_r$ into the solution group of $\LS$ follows the recipe given in the proofs of
Proposition~$4.8$, Lemma~$4.4$ and Proposition $4.2$ of Ref.~\cite{slofstra2017}.
The order of applying the results is the reverse of the order they are presented in Ref.~\cite{slofstra2017}.
We give details of this embedding process in \cref{sec:power2} for $r = 2$, \cref{sec:power3} for $r = 3$, 
and \cref{sec:power5} for $r = 5$.

@@

We start with proving that $\ket{x_{k_1}} = 0$.
Proving $\ket{x_{k_i}} = 0$ for other $i$ follows a similar argument, so we briefly
discuss about it in the end.
The entry $\bra{1}M\ket{1}$ can be expressed as  
\begin{align}
	\bra{1}M\ket{1} = \sum_{k=0}^{d-2}\sum_{l = 1}^{d-1}\sum_{i=1}^{d-1} x_{k, l}\omega_d^{il}\braket{1}{i/r^k}\braket{i}{1}.
\end{align}
For the term $\braket{1}{i/r^k}\braket{i}{1} \neq 0$ we must have $i = 1$ and $r^k \equiv 1 \pmod{d}$, or equivalently,
$k = k_1$. We can conclude that 
\begin{align}
	\bra{1}M\ket{1} = \sum_{l = 1}^{d-1} x_{k_1,l}\omega_d^l = 0. 
\end{align}
Similarly we can determine that for all $j = 1,2\dots d-1$,
\begin{align}
	\bra{j}M\ket{j} 
	=  \sum_{k=0}^{d-2}\sum_{l = 1}^{d-1}\sum_{i=1}^{d-1} x_{k, l}\omega_d^{il}\braket{j}{i/r^k}\braket{i}{j} 
	= \sum_{l = 1}^{d-1}x_{k_1,l}\omega_d^{jl} = 0.
\end{align}
Hence we get $d-1$ equations with $d-1$ variables, and the linear system is
\begin{align}
	W \ket{x_{k_1}} = 0,
\end{align}
where $W(m,n) = \omega_d^{mn}$. Then we define
\begin{align}
	\tW = 
	\begin{pmatrix}
	1 & 1 \\
	1 & W
	\end{pmatrix}.
\end{align}
First observe that $\tW$ is a Vandermonde matrix, hence it is non-singular.
Next, we define $\ket{\tx_{k_1}} = (0, x_{k_1,1}, \dots x_{k_1,d-1})^\intercal$ 
and prove that it satisfies the condition
that 
\begin{align}
	\tW \ket{\tx_{k_1}} = 0,
\end{align}
which involves $d$ equations. The last $d-1$ equations are given by the assumption and $M$.
We only need to prove that $\sum_{l=1}^d x_{k_1, l} = 0$, which is required by the first row of $\tW$.
It can be proved by summing the known $d-1$ equations as follows
\begin{align}
	0=\sum_{j = 1}^{d-1} \bra{j}M\ket{j}  
	=  \sum_{j=1}^{d-1}\sum_{l = 1}^{d-1}x_{k_1,l}\omega_d^{jl}
	=\sum_{l = 1}^{d-1}x_{k_1,l} (\sum_{j=1}^{d-1} \omega_d^{jl})
	= \sum_{l = 1}^{d-1}- x_{k_1,l}
\end{align}
where we have used the fact that $\sum_{j=1}^{d-1} \omega_d^{jl} =-1$ for all $l = 1,2\dots d-1$.
Since $\tW$ is non-singluar, we know $\ket{\tx_{k_1}} = 0$ which implies that $\ket{x_{k_1}} = 0$.
